Comprehensive optical and data management infrastructure for high-throughput light sheet microscopy of whole mouse brains

### 2015-02-11 latex-style-files-spie-manuscript/manuscript_Leo.tex
- merged with Ludo, new file name now Leo (something) - cosmetic changes to Ludo's parts - added Ludo's amazing new graph - think formulas in new tables were wrong (swapped exp time and shutter pace) - changed chip dimension to r because l is used for lines in confocal slit - changed number vertical pixels to number horizontal lines in table to match text - added abstract - adapted end of intro to new abstract - I like the new title - updated new line exposure time and consequently derived values - general spell and consistency checks - optical characterisation in next update - conclusion stil

\title{Robust data management for high through-put light sheet microscopy of whole mouse brains}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
200 words limit. no numerical references presenting concisely the objectives, methodology used, results obtained, and their significance.
\end{abstract}

%>>>> Include a list of up to six keywords after the abstract
\keywords{Light sheet microscopy, big data, whole brain mounting, data management, whole brain imaging, rolling shutter, 7,8.}

@@

The highly ambitious project of mapping and understanding each and every neuronal connection in the whole brain has been moved from the realm of wishful longing to feasible reality by the recent advent of light sheet fluorescent microscopy (LSFM). With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal and spine features in time scales which are no longer the bottle neck of high-throughput acquisition. In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}. This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate, perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap. Consequently fluorophores outside the light sheet are neither bleached nor contribute blurring out-of-focus noise. Consequently LSFM reduces phototoxicity and photobleaching while achieving excellent resolution at high penetration depths; however, it requires the sample to be transparent.

Several challenges remain to be overcome, however, to allow fast and, most of all systematic, production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks. Those challenges include fast, cheap and reproducible sample preparation, automated image acquisition that does not require constant attention by an expert and, most crucially, the storage, interpretation and analysis of the unprecedented huge data sets light sheet microscopy routinely produces. The mapping and understanding of this ``big data" is a colossal task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation. On the other hand, the imaging of large, intrinsically opaque samples in light sheet microscopy necessitates clearing protocols based on refractive index matching which render the tissue transparent. This makes LSFM a truly interdisciplinary field in which the technological advances by optical developers need to be matched by novel development in the area of information and biotechnology.

Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large, clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples. After briefly presenting the optical clearing protocol we employ to render our samples transparent, we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition to a full description of the optical setup, the control hardware and software, we further present a practical guide for the alignment of a LSFM, a non-trivial task that requires careful consideration. A systematic approach to handle, store and analyse the data is explained in detail. We further explain about the data volume we produce how it can be reduced and handled. The imaging capabilities are demonstrated by 3D reconstructions of biological specimens.  The final sentence of the introduction needs to be amazing.

@@

		\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame1.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:excitation} (A) Topview of the excitation path. The galvo scanners are mounted above periscopes. LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter, ABCD: flip mirrors. Inset: detection. (B) Oblique view of the microscope. A custom-made breadboard serves to mount the sample chamber and objectives at an elevated height and features two circular holes at the edges for the periscopes and a large central cut out for the translation stages. A second breadboard is used for the camera.} 
   \end{figure}

\subsection{Laser unit}		
The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system. First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. A digital line is used to electronically control the frequency with which the polarisation is changed. After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).

\subsection{Illumination unit}		
From here on three different light paths can be chosen through flip mirrors. One light path option guides the light through an axicon (apex angle of $160\degree$) and an achromatic doublet (f50) to create a Bessel beam. The other two options create Gaussian beams of different beam diameter. This diameter variation translates to different fields of view later on in the detection path. The three options are recombined before a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two identical excitation arms. The beam is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo). The galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.

The scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm). The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent. The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
Additionally each line is specimen is illuminated with the same intensity creating a homogeneous light sheet which is particularly advantageous for the quantitative investigation of large samples in their entirety.

@@

In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens for an image on a wide-field detector. Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. The cell size of the OrcaFlash is $p^2= 6.5\micro m$ x $6.5\micro m$ over an active area of 13.3mm. With a 200mm tube lens the field of view in the sample is $480\micro m$.

In the rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t=9.7\micro s$, see Table\ref{tab:resolution}) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to $l=3ms$ results in approx. $k=\nicefrac{l}{t}\approx300$  lines being simultaneously exposed at any time. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $d_s=\nicefrac{k p}{M_{\text{eff}}}= 0.72m$ in the sample space. With the given values of line exposure and line read out time, the camera acquires images at a frame rate of $\nu = \nicefrac{1}{(2048t+l)} \approx 44Hz$.

The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for a data acquisition and generation device (DAQ) from National Instruments which was operated as slave. The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012}. For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition. Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast. The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.

@@

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame2.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:frame2} Schematic of light sheet microscopy. (A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap. (B) The custom-made sample chamber is assembled with silicone bellows and seal rings. The clarified, fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber (C) and can be translated and rotated freely with piezo motors (D). (E) Mounting of a clarified, fluorescently labelled brain. The brain is glued onto a coverslip and inserted into an adapter that slides into the Teflon cylinder.} 
   \end{figure}

@@

For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:frame2},D). The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip. The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw. The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective. Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.

We designed a cubic, water-tight sample chamber (Figure\ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:frame2},B). All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:frame2},C). The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45. To fill the entire volume of the sample chamber approximately 400ml clearing solution are needed. A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of the Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:frame2},D). Illumination and detection axes are horizontal and the sampler rotation occurs around the vertical axis.

\section{Optical characterisation}
An overview of imaging properties and derived quantities is given in Table\ref{tab:resolution}.

@@

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{connectivity.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:connectivity} Schematic views of the hardware (A) and software (B) architectures of the microscope, showing physical and logical connections, respectively. The software architecture scheme clarifies the hierachic structure of the Murmex components. AO analog output, DO digital output, DI digital input.} 
   \end{figure}

@@

The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated together and operated through a custom-made software. Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing proper synchronization, software design is not a secondary issue when building a light sheet microscope for whole-brain imaging. The overall architecture of the software and its practical implementation were chosen to satisfy several principles:

\begin{itemize}
\item{\emph{User-friendliness}. The light sheet microscope here presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment. The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by researchers with no expertise in optics and/or software development.}
\item{\emph{Working in a distributed environment}. The apparatus should deal with many independent hardware components, and with several data streams (see below). Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.}
\item{\emph{Robustness and ease of maintenance}. Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of precious data. Furthermore, developers must be able to fix existing code or to develop new one without having to change the whole software.}
\item{\emph{Reusability and scalability}. When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch is pure loss of time. Writing well structured, scalable and easily maintainable scientific software can help avoiding redundancy and boosting up productivity.}
\end{itemize}

Our microscope management software has been written in LabVIEW (National Instruments, Austin, US), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods. An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules. This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability. Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously. The graphical user interface (GUI) provides intuitive control of the apparatus as well as deep personalization. In general, the intrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided. Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{murmex.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:murmex} This graph needs a caption.} 
   \end{figure}

@@

Basically, Murmex creates distributed finite state machines. These are design patterns in which one component proceed from one particular state to another based on the message it receives either from itself or from other components. For sending and receiving messages, Murmex uses the library \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ}, which is a wrapper of \href{http://www.rabbitmq.com/}{RabbitMQ}, a message-oriented middleware facilitating message shipment and receival. These layers of abstraction are mostly hidden for the developers. The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network. The message-based communication allows for buffered, asynchronous and reliable message communication between several software components. Messages are routed by the broker to the specific software component by its ID. The LabbitMQ wrapper allows use of RabbitMQ inside the LabVIEW programming environment.

>>>>

\title{Comprehensive optical and data management infrastructure for high-throughput light sheet microscopy of whole mouse brains}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
The comprehensive mapping and quantification of neuronal connections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution. We have developed a confocal light sheet microscope that has been optimised for the 3D imaging of structurally intact, clarified, whole-mount mouse brains. Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software. The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.  It can easily be adapted and integrated to other microscope systems and has been made freely available to the light sheet community. The unprecedented amount of data routinely generated by light sheet microscopy further requires novel strategies for data handling and storage. To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching and visualisation of 3D data sets. The meso-scale neuroanatomy imaged at micron-scale resolution allows characterization and quantification of neuronal connections in unsectioned mouse brains. 
\end{abstract}

%>>>> Include a list of up to six keywords after the abstract
\keywords{Light sheet microscopy, whole brain mounting, whole brain imaging, big data, data management, software management, imaging pipeline, high-throughput imaging.}

@@

The highly ambitious project of mapping and understanding each and every neuronal connection in the whole brain has been moved from the realm of wishful longing to feasible reality by the recent advent of light sheet fluorescent microscopy (LSFM). With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal and spine features in time scales which are no longer the bottle neck of high-throughput acquisition. In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}. This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate, perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap. Consequently fluorophores outside the light sheet are neither bleached nor contribute blurring out-of-focus noise. Hence LSFM reduces phototoxicity and photobleaching while achieving excellent resolution at high penetration depths.

Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks. Those challenges include fast, cheap and reproducible sample preparation and mounting, automated image acquisition that does not require constant attention by an expert and, most crucially, the storage, interpretation and analysis of the unprecedented huge data sets light sheet microscopy routinely produces. The mapping and understanding of this ``big data" is a colossal task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation. On the other hand, the imaging of large, intrinsically opaque samples in light sheet microscopy necessitates clearing protocols based on refractive index matching which render the tissue transparent. This makes LSFM a truly interdisciplinary field in which the technological advances by optical developers need to be matched by novel development in the area of information and biotechnology.

Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large, clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples. After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition, a full description of the the control hardware and software is presented. The microscope software coordinates each and every microscope component and ensures critical timing and synchronisation between those components. The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light sheet community. We further give a systematic and robust approach to handle, store and analyse light sheet microscopy data of tens of terabytes. To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets.

@@

		\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame1.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:excitation} (A) Topview of the excitation path. The galvo scanners are mounted above periscopes. LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter. Inset: detection path. (B) Oblique view of the microscope. A custom-made breadboard serves to mount the sample chamber and objectives at an elevated height and features two circular holes at the edges for the periscopes and a large central cut-out for the translation stages. A second breadboard is used for the camera.} 
   \end{figure}

\subsection{Laser unit}		
The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system. First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. A digital line is used to switch to zero the output of the pre-amplifier, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing). After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).

\subsection{Illumination unit}		
The light impinges onto a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two identical excitation arms. The beam diameter is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo). Both galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.

Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).  The galvos are on planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen. The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent. A guide to align objectives to a common focus can be found in the supplementary information. The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts. %cite{StelzerNatMeth2014}.
Additionally each line in specimen is illuminated with the same intensity creating a homogeneous light sheet which is particularly advantageous for the quantitative investigation of large samples in their entirety.

@@

In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector. Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, effective focal length 7.2 mm). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$. With a 200mm tube lens the field of view in the sample is $480\micro m$ (see also Table \ref{tab:resolution} for relevant formulas).

In the camera's rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in approx. $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of

\begin{equation}
s_{\text{object}}=\frac{l p}{M_{\text{eff}}}= 7.2 \micro m 
\end{equation}

in the sample space, where $M_{\text{eff}}$ is the effective magnification of the detection objective. With the given values of line exposure and line read out time, the camera acquires images at a frame rate of

\begin{equation}
\nu = \frac{1}{(\#_{\text{horiz. lines}}*t_{\text{shutter}}+t_{\text{exp}})} \approx 50Hz. 
\end{equation}

The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for a data acquisition and generation device (DAQ) from National Instruments which was operated as slave. The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also paragraph \ref{sec:timing} on synchronisation). Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast. The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it the rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.

@@

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame2.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:frame2} Schematic of sample mounting and motion. (A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap. (B) The custom-made sample chamber is assembled with silicone bellows and seal rings. The clarified, fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber filled with clearing solution (C) and can be translated and rotated freely with piezo motors (D). (E) Mounting of a clarified, fluorescently labelled brain. The brain is glued onto a coverslip and inserted into an adapter that slides into the Teflon cylinder.} 
   \end{figure}

We designed a cubic, water-tight sample chamber (Figure\ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:frame2},B). All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:frame2},C). The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45. To fill the entire volume of the sample chamber approximately 400ml clearing solution are needed. A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:frame2},D). Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.

@@

For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:frame2},E). The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip. The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw. The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective. Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.

\section{Optical characterisation}

The optical properties of a microscope can be summarized by the point-spread function (PSF), which is the image of a point source in object space. In particular, the radial (i.e. perpendicular to the detection axis) and axial (i.e. parallel to the detection axis) resolution of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction. In a light sheet microscope, axial and radial resolutions are determined by the numerical aperture (NA) of the illumination and detection optics, respectively. The radial PSF is a standard Airy function, whose FWHM is given by:

\begin{equation}
\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}} \, ,
\end{equation}

$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective.

The axial resolution is given by the thickness of the light sheet. If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}. The $1/e^2$ radius of the beam waist is given by:
\begin{equation}
w_0 = \frac{\lambda f_{\text{i}}^{\text{eff}}}{\pi w} \, ,
\end{equation}
where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index). Note that, for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from unity\cite{Silvestri2012}.
The axial FWHM is then given by:
\begin{equation}
\text{FWHM}_{\text{axial}} \simeq 1.177 w_0 \, .
\end{equation}

The thickness of the light sheet is not constant throughout the field of view due to the limited depth of focus of the Gaussian beam. This latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius is not bigger than $\sqrt{2} w_0$:
\begin{equation}
b = \frac{2\pi w_0^2}{\lambda} = \frac{2 \lambda  {(f_{\text{i}}^{\text{eff}})}^2}{\pi w^2}\, .
\end{equation}

The need to have an almost uniform resolution in the camera field of view (FOV) imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution. In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq ???$, resulting in $b \simeq ???$ and $\text{FWHM}_{\text{axial}} \simeq?????$.

An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table\ref{tab:resolution}. The reader is referred to this table as a quick guide to tailor the apparatus to their specific needs.

AND HERE THE AMMAZING OURS DATAS

@@

For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition.

@@

@@

The many components of the microscope (camera, lasers, AOTF, stages, etc.) are orchestrated and operated through a custom-made software. Since the microscope should work mainly without human intervention for many hours (a whole-brain tomography can last a couple of days) without losing precise synchronization, software design is not a secondary issue when building a light sheet microscope for whole-brain imaging. The overall architecture of the software and its practical implementation were chosen to satisfy several principles:

\begin{itemize}
\item{\emph{User-friendliness}. The light sheet microscope presented was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment. The greatest challenge therefore consists in making the use of the microscope easy and intuitive such that no formidable proficiency is needed when it is operated by researchers with no expertise in optics and/or software development.}
\item{\emph{Working in a distributed environment}. The apparatus should deal with many independent hardware components, and with several data streams (see below). Individual processing steps and/or data transfer can be computationally intensive, and may need to be distributed over several computers to perform properly at run-time.}
\item{\emph{Robustness and ease of maintenance}. Any kind of hardware problem, from timing delay to real failure, must be automatically handled to avoid loss of precious data. Furthermore, developers must be able to fix and expand existing code without having to change the whole software.}
\item{\emph{Reusability and scalability}. When a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same or in other laboratories, re-writing all the code from scratch represents extensive but avoidable loss of time. Writing well structured, scalable and easily maintainable scientific software can help preventing redundancy and boosting up productivity.}
\end{itemize}

Our microscope management software has been written in LabVIEW (National Instruments, Austin, US), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods. An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules. This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability. Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously. The graphical user interface (GUI) provides intuitive control of the apparatus as well as full personalisation. In general, the instrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided. Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{murmex.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:murmex} Schematic view of the work flow of a representative Murmex component operating a camera.} 
   \end{figure}

@@

Basically, Murmex creates distributed finite state machines. These are design patterns in which one component proceeds from one particular state to another based on the message it receives either from itself or from other components. For sending and receiving messages, Murmex uses the library \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ}, which is a wrapper of \href{http://www.rabbitmq.com/}{RabbitMQ}, a message-oriented middleware facilitating message shipment and receival. These layers of abstraction are mostly hidden for the developers. The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network. The message-based communication allows for buffered, asynchronous and reliable message communication between several software components. Messages are routed by the broker to the specific software component by its ID. The LabbitMQ wrapper allows use of RabbitMQ inside the LabVIEW programming environment.
